\documentclass{beamer}

\title{Peer Review: A Guide for First-Time Reviewers}
\author{Naeem Abbasi}
\date{Nov 23, 2024}

\begin{document}

\frame{\titlepage}

\begin{frame}{What is Peer Review?}
    \begin{itemize}
        \item Experts evaluate the work of others for correctness and quality before publication.
        \item Familiarity with this process helps improve your own paper submissions.
    \end{itemize}
\end{frame}

\begin{frame}{What is a Double-Blind Review?}
    \begin{itemize}
        \item Neither the author nor the reviewer knows each other's identity.
        \item This ensures fairness and impartiality.
    \end{itemize}
\end{frame}

\begin{frame}{What to Look For When Reviewing a Paper?}
    \begin{itemize}
        \item \textbf{Motivation}: Why the problem matters and the importance of the results.
        \item \textbf{Problem Statement}: The specific problem being addressed.
        \item \textbf{Approach}: How the authors tackle the problem or make progress.
        \item \textbf{Results}: Key findings and their significance.
        \item \textbf{Conclusions}: Broader implications and relevance.
    \end{itemize}
\end{frame}

\begin{frame}{What Should Be in a Good Review?}
    \begin{itemize}
        \item \textbf{Short Summary}: Problem statement, approach, contributions, and results.
        \item \textbf{Questions for Authors}: Clarify unclear elements.
        \item \textbf{Editorial Comments}: Grammar, spelling, and completeness (figures, tables, equations, references).
    \end{itemize}
\end{frame}

\begin{frame}{Feedback to Authors and Committee}
    \begin{itemize}
        \item Feedback to Authors: Improve clarity, address weaknesses, and enhance technical quality.
        \item Feedback to Committee: Decision on acceptance, relevance, originality, accuracy, and clarity.
    \end{itemize}
\end{frame}

\begin{frame}{Submitting the Review}
    \begin{itemize}
        \item Use tools like EasyChair for formal submissions.
        \item Key elements: Decision, confidence, relevance, originality, clarity, references, and presentation recommendation.
    \end{itemize}
\end{frame}

\begin{frame}{Thank You}
    \begin{itemize}
        \item Thank you for participating in this volunteer activity.
        \item Your contributions are valuable to the academic community.
        \item Reach out with questions or concerns about the process.
    \end{itemize}
\end{frame}

\end{document}
